Neural models for computer-assisted musical orchestration: a preliminary study

### 2020-05-12 paper/latex/paper.tex
Make diagram full page
re commit model part

\begin{figure}
\includegraphics[scale=0.45]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure}

Given that audio is one kind of sequential data, it is easy to consider Long Short-Term Memory network(LSTM) as test model. In our setting, we added one LSTM layer with 32 outputs units following three convolutional layers following the same pattern as the CNN described earlier. After LSTM layer, we reshaped the output into the same size as the output of the last convulational layer, which was fed to another convolutional layer with the same structure and kernel size, yielding a tensor of dimensions $32\times 8 \times 21$. Finally, we flattened out the outputs and fed them into fully a connected layer with Dropout layer, followed by another fully connected layer. Finally, the sigmoid function was applied to th final layer in order to get a probability between 0 and 1 for each individual label.\\

@@

$$
\delta_{k1} = 
\begin{cases}
1, \text{if   } x_k > \tilde{x}_k \\
0, \text{otherwise}
\end{cases} 
$$

$$
\delta_{k2} = 
\begin{cases}
1, \text{if   } x_k < \tilde{x}_k \\
0, \text{otherwise}
\end{cases} 
$$

This metric computes the difference between the FFT of the target and the FFT of the solution.

>>>>

\begin{figure*}
\includegraphics[scale=0.45]{CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{figure*}

Given that audio is one kind of sequential data, it is easy to consider Long Short-Term Memory network(LSTM) as test model. In our setting, we added one LSTM layer with 32 outputs units following three convolutional layers following the same pattern as the CNN described earlier. After LSTM layer, we reshaped the output into the same size as the output of the last convulational layer, which was fed to another convolutional layer with the same structure and kernel size, yielding a tensor of dimensions $32\times 8 \times 21$. Finally, we flattened out the outputs and fed them into fully a connected layer with Dropout layer, followed by another fully connected layer. Finally, the sigmoid function was applied to the final layer in order to get a probability between 0 and 1 for each individual label. Since there is no competition relationship between different classes for each class can be classification result equally, it is reasonable for us to take sigmoid activations and used binary classification for each class to treat them independently. We minimize the binary cross entropy(BCE) loss between the predictions and targets. We implemented our neural networks with PyTorch and trained them with Adam optimizer. The model architecture is shown in Figure\ref{cnn_lstm}.\\

@@

\begin{equation}
\delta_{k1} = 
\begin{cases}
1, \text{if   } x_k > \tilde{x}_k \\
0, \text{otherwise}
\end{cases} 
\end{equation}

\begin{equation}
\delta_{k2} = 
\begin{cases}
1, \text{if   } x_k < \tilde{x}_k \\
0, \text{otherwise}
\end{cases}
\end{equation}

This metric takes in the FFT of the target, $x$ and the FFT of the solution $\tilde{x}$ and computes the difference between them at each bin.
